Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-12 paper.tex
rewrote one sentence in introduction

Coordinating a multi-agent system of intelligent situated agents is a traditional research problem, 
impacted by the challenges posed by the very notion of distributed intelligence.  \lukas{what are these challenges?}
%
The problem is even more evident in large-scale collective adaptive systems, 
where agent interactions are necessarily proximity-based, thus making the emergence of controlled global collective behaviour harder. \lukas{what does it make harder?}
% 
In this context, two main approaches have been proposed for creating distributed controllers out of macro-level task/goal descriptions: 
 \emph{manual design}, in which programmers build the controllers directly, and 
 \emph{automatic design}, which involves synthesizing programs using machine learning methods.
%
In this paper, we consider a new \emph{hybrid} approach called  \emph{Field-Informed reinforcement learning}, 
  which uses manually designed \emph{computational fields} (globally distributed data structures) to manage the interaction between agents and a \emph{reinforcement learning technique} in combination with \emph{Graph Neural Networks} to learn the local behaviour necessary to solve collective tasks. 
%
This allows us to create distributed controllers informed by a collective knowledge 
 that has been distilled during learning, but that uses only local information at runtime.
% 
We demonstrate the effectiveness of this new approach in simulated use cases 
 where tracking and covering tasks for swarm robotics are successfully solved. 
\end{abstract}

@@

Let $\Gamma$ be the aggregate program that runs take $G_t$ as input.  \lukas{$G_t$ is not defined. also, not sure what `runs against' means - take $G_t$ as input?}

>>>>

Coordinating a multi-agent system of intelligent situated agents is a traditional research problem, 
impacted by the challenges posed by the very notion of distributed intelligence.  \lukas{what are these challenges?}
%
The problem is even more evident in large-scale collective adaptive systems, 
where agent interactions are necessarily proximity-based, thus making the emergence of controlled global collective behaviour harder. \lukas{what does it make harder?}
% 
In this context, two main approaches have been proposed for creating distributed controllers out of macro-level task/goal descriptions: 
 \emph{manual design}, in which programmers build the controllers directly, and 
 \emph{automatic design}, which involves synthesizing programs using machine learning methods.
%
In this paper, we consider a new \emph{hybrid} approach called  \emph{Field-Informed reinforcement learning}. We utilise manually designed \emph{computational fields} (globally distributed data structures) to manage the interaction between agents. Using \emph{Deep Q-learning} in combination with \emph{Graph Neural Networks} we enable the agents to learn the necessary local behaviour automatically to solve collective tasks. 
%
This allows us to create distributed controllers informed by a collective knowledge 
 that has been distilled during learning, but that uses only local information at runtime.
% 
We demonstrate the effectiveness of this new approach in simulated use cases 
 where tracking and covering tasks for swarm robotics are successfully solved. 
\end{abstract}

@@

Let $\Gamma$ be the aggregate program that takes $G_t$ as input. 
% \lukas{$G_t$ is not defined. also, not sure what `runs against' means - take $G_t$ as input?}
